\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}

\usepackage{alltt}
\usepackage{float}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{amssymb} % for math symbols
\usepackage{amsmath} % for aligning equations
\usepackage{textcomp}
\usepackage{natbib}
\topmargin -1.5cm        
\oddsidemargin -0.04cm   
\evensidemargin -0.04cm
\textwidth 16.59cm
\textheight 21.94cm 
%\pagestyle{empty} %comment if want page numbers
\parskip 7.2pt
\renewcommand{\baselinestretch}{1.5}
\parindent 0pt
\usepackage{blindtext}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\title{Smithers - 2023 - Dailylog}

\author{Deirdre Loughnan}

\begin{document}

\maketitle
\section{Camping and travel notes}

\subsection{Travel}

If you are doing the drive over two days, DO NOT stay at the Whispering willows campsite north of Williams lake. Despite the reviews, it did not appear maintained at all and was so close to the highway sleep was difficult. In terms of nice motels, the Bear Claw lodge in Cache creek was simple, with small rooms, but nice overall. The Sandman inn in Smithers is also a good, if slightly expensive option. Planning ahead may be necessary, as motels tend to fill with fire fighters in the summer. 

\subsection{Camping}

I liked camping, even more so than Bob's cabin. The two options are the Smithers Municipal campground, located on the edge of town beside the river. There are three tiers of campsites, including tenting for \$26 a night. The campsite is an open field, so little privacy, but it does include showers (\$1 for 5 min) and wifi. The other option is the Tyhee Provincial Park. This is more of a drive (10min), in Houston. It is similar in price, but a more forested area offering more privacy. It also has showers, but no wifi. There is a lake in the park for swimming though!

\section{July 27, 2023}

First day in the field. Weather was rainy, but not miserably so. Resampled plot JCHM 1, 7, 8, 11, 2. 

2A - one tag moved

7F - large tree fallen on it, crushed plot

8A -  tags moved, found together on ground
8C - one tag moved

11A - one tag moved
11D - one tag moved
11F - both tags moved - just established a new plot

\section{July 28, 2023}
Weather today was great, it rained in the morning but became sunny and not too hot in the afternoon. We sampled plots 5, 15,17, 12.

5A - one tag moved

15B - one tag moved

17A - one tag moved
17C - markers lost, established new plot

12F - one tag moved, found laying on the ridge

\section{July 30, 2023}
Weather today was very nice, sunny and warm. We sampled plots 9, 16, 14,  6.

6B - tag moved
6D - heavily disturbed

9B - one tag moved
9F - Both tags moved

14B - one dislodged tag; heavily disturbed with many fallen trees

\section{July 31, 2023}
Great luck today, it was supposed to thunder, but we were able to finish before the storm hit. Sampled plots 4, 10, 13, and 3.

10F - one tag moved




\end{document}