\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}

\usepackage{alltt}
\usepackage{float}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{amssymb} % for math symbols
\usepackage{amsmath} % for aligning equations
\usepackage{textcomp}
\usepackage{natbib}
\topmargin -1.5cm        
\oddsidemargin -0.04cm   
\evensidemargin -0.04cm
\textwidth 16.59cm
\textheight 21.94cm 
%\pagestyle{empty} %comment if want page numbers
\parskip 7.2pt
\renewcommand{\baselinestretch}{1.5}
\parindent 0pt
\usepackage{blindtext}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\title{Smithers - 2022 - Dailylog}

\author{Deirdre Loughnan}

\begin{document}

\maketitle
\section{Pre-fieldwork notes}

The order of the sites we sample this year will be:  3,  9, 12, 5  -- 7, 13, 10,  4 -- 11, 17, 6, 2 --  8, 15, 14, 1 -- 13, 16. To find the trail head, follow signs for Driftwood Canyon, but continue up the road until you cross the bridge and arrive at the Harvey Mt. trailhead. 

\section{July 15, 2022}

First day in the field! The weather was very wet, with it raining all day, because of this we ended the day early (8:15 am to 3:30pm).

\begin{itemize}
\item Resampled plot JCH4, 9, 11, 5, 3, 1 ...
\end{itemize}
\section{July 16, 2022}

Today the weather was nicer, but we still had some light rain in the afternoon. The forest was very wet from last nights rain and therefore I do not think we should measure soil moisture until Monday at the earliest.

\begin{itemize}
\item Sampled plots: JCH6, 8,10, 12, 14, 13, 7, 2
\end {itemize}

\section{July 17, 2022}

Finished sampling, completing plots 16, 15, 17. The hike was very tiresome, but the weather held out and it was actually very clear and sunny for a change. The ground remains very wet though, and the trail was exceedingly muddy in places. 

\section{July 18, 2022}

We de-tagged Darwin's unused plots from the community forest. But the GPS did not have any of the other plots and we were unable to find the plots at Sun King. I also did not know what plots were LT or MO (mount onion perhaps).

Upon returning to Vancouver, I caught up with Darwin and he said that there are a few plots on Mt. Onion. So someone in a future year will have to take the tags down from there.

\end{document}